---
title: "Analysis of Film and Music Sales for Media Distributors, Inc."
author: "Nitika "
date: "Spring 2025"
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
    toc_float: true
    theme: paper
    highlight: tango
    df_print: kable
    code_folding: hide
    keep_md: true
    fig_width: 8
    fig_height: 5
    fig_caption: true
  word_document:
    toc: true
    toc_depth: '2'
  pdf_document:
    toc: true
    toc_depth: '2'
subtitle: Prepared by Oakland Partners
---

```{r setup, include=FALSE}
library(DBI)
library(RMySQL)
library(knitr)
library(kableExtra)
con <- dbConnect(RMySQL::MySQL(),
                 dbname = "defaultdb",
                 host = "cs5200-practicum-2-njain980316-ab68.i.aivencloud.com",
                 port = 28549,
                 user = "YOUR_PWD",
                 password = "AVNS_aaxYX8Qu3vXWhFDcv1k")
```

# Introduction

This report summarizes sales insights from the integrated film and music operational databases for Media Distributors, Inc. Our goals include understanding product performance by time and country, identifying revenue trends, and profiling our customer base.

# Total Revenue by Country and Product Type

```{r, echo=FALSE}
query <- "
SELECT country_id, product_type, SUM(total_revenue) AS total_revenue
FROM fact_sales_summary
GROUP BY country_id, product_type
ORDER BY total_revenue DESC
LIMIT 10"
df <- dbGetQuery(con, query)
kable(df, caption = "Top 10 Country/Product Combinations by Revenue") %>%
  kable_styling("striped", full_width = F)
```

# Revenue Trends Over Time

```{r, echo=FALSE}
query <- "
SELECT year, quarter, product_type, SUM(total_revenue) AS total_revenue
FROM fact_sales_summary f
JOIN dim_time t ON f.time_id = t.time_id
GROUP BY year, quarter, product_type
ORDER BY year, quarter"
df <- dbGetQuery(con, query)
kable(df, caption = "Quarterly Revenue Trends") %>%
  kable_styling("striped", full_width = F)
```

# Average Revenue Per Sale by Country

```{r, echo=FALSE}
query <- "
SELECT country_id, product_type,
       ROUND(SUM(total_revenue) / SUM(total_units_sold), 2) AS avg_revenue_per_sale
FROM fact_sales_summary
GROUP BY country_id, product_type
ORDER BY avg_revenue_per_sale DESC
LIMIT 10"
df <- dbGetQuery(con, query)
kable(df, caption = "Top Countries by Avg Revenue per Sale") %>%
  kable_styling("striped", full_width = F)
```

# Customer Base by Country and Type

```{r, echo=FALSE}
query <- "
SELECT dc.country_id, dc.customer_type, COUNT(*) AS num_customers
FROM dim_customer dc
GROUP BY dc.country_id, dc.customer_type
ORDER BY num_customers DESC"
df <- dbGetQuery(con, query)
kable(df, caption = "Customer Distribution by Country and Type") %>%
  kable_styling("striped", full_width = F)
```


